Efficiently Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-13 robdml.tex
tex

In literature, various triplet sampling strategies exist, such as random,
semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance},
and the hardest negative sampling (\ie, the negative sample with the largest
loss value).
%
Although any of them can be selected for source or destination hardness for HM,
not all the possible combinations are expected to be effective or efficient.
%
In order to figure out an empirically good combination of source and
destination hardness, we adversarially train RN18 models on the CUB dataset
with every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.
%
Note, these methods are empirically sorted by their expectation of hardness
$E[H]$, in the ascending order: random, semihard, softhard, distance, and
hardest.

@@

To figure out an appropriate combination for further experiments, we try
every possible combination and compare their R@1 and ERS performance, as
shown in \cref{tab:desth}.
%
\oo{The table suggests that}

The proposed hardness manipulation is effective.
\oo{todo: table of first and second order central moment}

>>>>

In literature, various triplet sampling strategies exist, such as random,
semihard~\cite{facenet}, softhard~\cite{revisiting}, distance~\cite{distance},
and the hardest negative sampling (\ie, the negative sample with the largest
loss value).
%
Although any of them can be selected for source or destination hardness for HM,
not all the possible combinations are expected to be effective or efficient.
%
In order to figure out an empirically good combination of source and
destination hardness, we adversarially train RN18 models on the CUB dataset
with every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.
%
Note, these methods are empirically sorted by their expectation of hardness
$E[H]$, in the ascending order: random, semihard, softhard, distance, and
hardest.
%
\oo{todo: table of first and second order central moment}

@@

% 4. summary

In summary, according to \cref{tab:desth}, HM from random to semihard, or from
softhard to semihard are two choices that can effectively lead to robust
DML model.
%
The subsequent experiments will be based on the two choices.
